Wireless smart monitoring energy system: a proof of concept

### 2021-03-17 paper/main.tex
push

\section{System results}

\section{Consumption}
%Qui mettiamo workflow generale con immagine algoritmo

>>>>

\section{System results}
We use Wireshark to monitor our network, while there was intensive traffic over the wireless connection - such as Netflix 1080p streaming (UDP traffic) and a download of Ubuntu operating system ISO (TCP traffic). As we know the consistence of miscellaneous traffic type is not very well managed by wireless protocols, our measurements have the scope to guarantee the reliability of our ACK implementation - even only with two smart plugs. The packets are sent to the correct client on average within 3.3 ms.
 \section{Consumption}
%Qui mettiamo workflow generale con immagine algoritmo
